%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Sponsorship \& Fundraising Officer} % Affiliation/role
    {Edinburgh University Swimming and Water Polo Club} % Organization/group
    {Edinburgh, SCOTLAND} % Location
    {Sept. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item I negotiated with two local bars to sponsor EUSWPC for the academic year. This will be an immense help in paying for pool time, coaches, travel to competitions and much more.
        \item I led the club's Movember campaign, raising over £300 for 'Health in Mind' - a locally based mental health charity in Edinburgh.
        \item I organised and created a 2022 calendar with photographs of some of our club members, with all proceeds also going to Health in Mind. In total I sold over 45 copies, which raised £315.
        \item Currently leading a week-long blood drive in association with GiveBlood4Good and all social medoa posts.
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Social Secretary} % Affiliation/role
    {Edinburgh University Swimming and Water Polo Club} % Organization/group
    {Edinburgh, SCOTLAND} % Location
    {Sept. 2020 - May 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item I organised online social events for our club, of over 150 members, during the height of the Covid pandemic.
        \item I led the club's Movember campaign and managed all social media posts. In total, we raised over £1000 for Health in Mind.
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Men's Captain - Club Squad} % Affiliation/role
    {Edinburgh University Swimming and Water Polo Club} % Organization/group
    {Edinburgh, SCOTLAND} % Location
    {Sept. 2019 - May 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item I captained a squad of more than 20 swimmers for university swimming matches
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
